The Inner Mass-Ratio Distribution of Intermediate-Mass Stars

### 2016-01-21 paper/ms.tex
Wrote initial draft of paper introduction

@@

Multiplicity is an inevitable outcome of star formation, especially for more massive stars where multiplicity is more common \citep{Zinnecker2007}, and so is important to study in its own right. Beyond the overall multiplicity rate, the mass ratio, period, and eccentricity distributions of a binary star population can place important constraints on the mode of binary star formation. Specifically, a mass-ratio distribution that changes with physical separation could indicate that secondary stars are either forming through disk fragmentation \citep[e.g.][]{Kratter2006, Stamatellos2011}  or are accreting a significant amount of their mass from the primary star disk. \cite{DeRosa2014} recently completed an imaging survey of nearby A-type stars, and found preliminary evidence that the mass-ratio distribution does in fact become flatter for closer companions. There is no evidence of such a change for solar-type or later stars \citep{Meyer2013}.

It is difficult to detect low-mass companions very near an intrinsically bright primary star and even more difficult to characterize the companion. There are three commonly used techniques for binary star searches: direct imaging with adaptive optics systems,  interferometry, and radial velocity monitoring. Imaging can easily detect low-mass companions at wide apparent separations, but loses sensitivity as the on-sky distance from the primary star decreases \citep[see][for typical sensitivity curves]{DeRosa2014}. Interferometry can usually achieve smaller working angles than imaging, but cannot achieve as high contrast \citep[see e.g.][]{Aldoretta2015}.

 Radial velocity monitoring can easily find companions on very short-period orbits, but its sensitivity to low-mass companions drops as the physical separation increases. This is especially true for A- and B-type stars, where radial velocity precision is typically limited to $\sim 1 \rm km \  s^{-1}$ by their rotationally broadened lines. Worse, radial velocity monitoring techniques cannot characterize the companion unless the inclination is known or if the companion spectral lines are also visible. All three techniques have separation-dependent sensitivity, which introduces observational bias in any search for a parameter that changes with physical separation.

 One technique that is separation independent is to search directly for the composite spectrum of two stars. \citet{Burgasser2007} used single-epoch low-resolution spectroscopy to identify and characterize a brown dwarf binary system by fitting both spectra simultaneously. This method only works if the stars have a similar brightness but very different spectra, such that the spectral features from both components are visible and distinguishable. If, as in the case of binary systems with very large flux ratios, the companion spectrum is buried within the noise of the primary star, a different method is needed.

The direct spectral detection method (hereafter referred to as the DSD method), and variations thereof, has been used to search for binary companions to early B-stars \citep{Gullikson2013}, main sequence FGK-stars \citep{Kolbl2015}, young K-M stars \citep{Prato2002}, and even `Hot Jupiter' type planets \citep{Snellen2010, Brogi2012, deKok2013} orbiting FGK-stars. The method relies on the cross-correlation function (CCF) of a high-spectral-resolution spectrum of the primary star with a model spectrum for the expected companion. The CCF uses every pixel in the spectrum, and more importantly every spectral line in the secondary spectrum. A simple experiment with synthetic spectra containing increasing numbers of spectral lines (N) in noisy data shows that the CCF peak significance increases as $\sim\sqrt{N}$. For high-resolution cross-dispersed \'echelle spectra, this amplification can reach several factors of 10, allowing the detection \emph{and characterization} of a secondary spectrum where the individual lines are completely buried in noise. Since the DSD method uses a seeing-limited spectrum of the primary star, its sensitivity is independent of separation inside $\sim 1 ''$ and can make use of small telescopes to detect high-contrast companions.

In this paper, we describe the DSD method in detail, and use it to detect the secondary star in nine known binary systems. We describe the method in Section \ref{sec:method}. We describe the observations and data reduction in Section \ref{sec:obs}, then use the observations to estimate the accuracy with which we can measure the companion temperature in Section \ref{subsec:systematics} and the sensitivity of the method in Section \ref{subsec:sensitivity}. In Section \ref{sec:results} we use the DSD method to search for known companions, and discuss the results in Section \ref{sec:conclusions}.

>>>>

Beyond the overall multiplicity rate, the mass ratio, period, and eccentricity distributions of a binary star population place important constraints on the mode of binary star formation. Most binary stars are thought to form via core fragmentation \citep{Boss1979, Boss1986, Bate1995}, in which a collapsing core fragments into two or more individual protostars. The number and initial masses of the fragments are set by the total core mass, as well as its rotation, turbulence, and its temperature and density structure. If the fragments are separated by $\gtrsim 1000$ AU, they will evolve relatively independently of each other, accreting mass from the core material onto their own protostellar disks and then onto the protostars themselves. However close fragments ($a \sim 100$ AU) will interact with each other; the protostellar disk may be truncated, destabilized, or even merge into a circumbinary disk if the separation is small enough. In addition, unstable disk can fragment to form low-mass companions \citep{Kratter2006, Stammatellos2011}. The mass ratios of close companions formed via either mechanism should be effected by preferential accretion. Most work has suggested that the disk material will preferentially accrete onto the lower mass companion \citep{Bate1997, BBB2002}; however, recent work has indicated that magnetic disk braking may result in preferential accretion onto the more massive component \citep{Zhao2013} instead. In either case, we would expect to find a different mass ratio distribution for companions inside a few $100$ AU and companions on wider orbits.

The mass ratio, period, and eccentricity distributions are fairly well-known for solar type stars \citep{Duquennoy1991, Raghavan2010} and cooler stars \citep{Fischer1992, Delfosse2004}. Interestingly, the mass ratio distribution appears to be invariant to separation for these stars \citep{Meyer2013}, contrary to the theoretical expectations. All of the distributions are much less certain for more massive stars. The reason for this is two-fold: first, more massive stars tend to more rare and farther away, meaning many of the companions are angularly close to the very bright primaries. Second, the primary stars tend to be rapid rotators, which limits radial velocity precision to $\sim 1 \mathrm{km\ s}^{-1}$. Worse, radial velocity monitoring can only measure a mass ratio if spectral lines from both components are visible; this typically suffers from the same flux ratio difficulty as imaging techniques. Nonetheless, \citet{DeRosa2014} performed an adaptive optics imaging survey of nearby A-type stars and found initial evidence that the mass ratio distribution for companions inside $125$ AU is much flatter than that of wide companions. Unfortunately they had only very few detections at these near separations, and the result is complicated by the inherent difficulty of detecting close companions with low mass ratios in an imaging survey.

In this paper, we describe a spectroscopic survey of nearby intermediate-mass stars. We search for companions using the direct spectral detection technique \citep{Gullikson2016}, which has a separation-invariant detection rate for all separations inside $\sim 1 ''$. We describe the stellar sample and data used for the survey in Section \ref{sec:obs}, as well as the data reduction steps in the same section. Next, we describe our estimation of the stellar parameters for the primary stars in our sample in Section \ref{sec:sp}. We then describe the direct spectroscopic detection and tabulate the companion detections in Section \ref{sec:companions}, and discuss the survey completeness in Section \ref{sec:completeness}. Finally, we end with a derivation of the mass ratio distribution from our sample in Section \ref{sec:mrd} and discuss its implications for binary formation in Section \ref{sec:discussion}.

@@
